analysis-pilot

### 2023-08-17 code/analysis-pilot.Rmd
line plots

#so like a third mismatch, and only a couple off by more than 1
```
# Prep accuracy

>>>>

#so like a third mismatch, and only a couple off by more than 1
```
partner 1:
id13
id15
id19
id21
id24
id26
id28
id30
id32
id33
id35
id39
id42
id43
id45
id47
id50
id52
id54
id58

partner 2:
id14
id16
id20
id22
id23
id25
id27
id29
id31
id34
id36
id40
id41
id44
id46
id48
id49
id51
id53
id57

# timed_transcripts editing for partner1
```{r}
timed_new <- timed_transcripts %>% 
  filter(!speaker %in% c("I", "M", "i", "id14", "id16", "id20", "id22", "id23", "id25", "id27", "id29", "id31", "id34", "id36", "id40", "id41", "id44", "id46", "id48", "id49", "id51", "id53", "id57")) %>% 
  filter(!trialNumStart %in% c(0.0, 0.5, 1.0, 13.0, NA)) %>% 
  mutate(wordCount = str_count(text, "\\S+"), roundStart = ceiling(trialNumStart)) %>% 
  filter(!roundStart %in% c(2.0, 4.0, 6.0, 8.0, 10.0, 12.0)) %>% 
  group_by(game, roundStart) %>% 
    summarize(totwordCount = sum(wordCount))

View(timed_new)

# timed_new graphing - left in speaker1listener
```{r}
ggplot(timed_new, aes(x = roundStart, y = totwordCount, group = game, color = game)) + 
  geom_line() +
  #geom_smooth() +
  labs(color = "Game ID", x = "\nRound #", y = "Utterance Count\n") +
  scale_x_continuous(breaks=seq(3,13,2), limits = c(3,13)) +
  scale_y_continuous(breaks=seq(0,30,1), limits = c(0,30)) +
  theme_classic() +
  theme(aspect.ratio = 9/9,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.title=element_text(size=13,face="bold"),
        legend.text=element_text(size=9),
        legend.position="right")
```
# timed_transcripts editing for partner2
```{r}
timed_neww <- timed_transcripts %>% 
  filter(!speaker %in% c("I", "M", "i", "id13", "id15", "id19", "id21", "id24", "id26", "id28", "id30", "id32", "id33", "id35", "id39", "id42", "id43", "id45", "id47", "id50", "id52", "id54", "id58")) %>% 
  filter(!trialNumStart %in% c(0.0, 0.5, 1.0, 13.0, NA)) %>% 
  mutate(wordCount = str_count(text, "\\S+"), roundStart = ceiling(trialNumStart)) %>% 
  filter(!roundStart %in% c(3.0, 5.0, 7.0, 9.0, 11.0, 13.0)) %>% 
  group_by(game, roundStart) %>% 
    summarize(totwordCount = sum(wordCount))

View(timed_neww)

# timed_neww graphing - left in speaker2listener
```{r}
ggplot(timed_neww, aes(x = roundStart, y = totwordCount, group = game, color = game)) + 
  geom_line() +
  #geom_smooth() +
  labs(color = "Game ID", x = "\nRound #", y = "Utterance Count\n") +
  scale_x_continuous(breaks=seq(2,12,2), limits = c(2,12)) +
  scale_y_continuous(breaks=seq(0,30,1), limits = c(0,30)) +
  theme_classic() +
  theme(aspect.ratio = 9/9,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.title=element_text(size=13,face="bold"),
        legend.text=element_text(size=9),
        legend.position="right")
```

# Prep accuracy
